Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-10 paper.qmd
Updated layout a link in PBMC3k

- Make sure langevitour is explained before using it (introduced in page 5)
- Too much code needs to be streamlined
- Remove all the extraneous commented text (Done)
- Check how \kD{} and \gD{} are used, and make sure it's sensible
- Check spelling is consistently American

@@

error_pbmc_umap <- read_rds("data/pbmc3k/error_pbmc_umap_30_min_dist_0.3.rds")
error_pbmc_umap2 <- read_rds("data/pbmc3k/error_pbmc_umap_5_min_dist_0.01.rds")
# error_pbmc_umap3 <- read_rds("data/pbmc3k/error_pbmc_umap_12_min_dist_0.99.rds")
# error_pbmc_umap3 <- read_rds("data/pbmc3k/error_pbmc_umap_3_min_dist_0.6.rds")
# error_pbmc_umap3 <- read_rds("data/pbmc3k/error_pbmc_umap_4_min_dist_0.6.rds")
# error_pbmc_umap3 <- read_rds("data/pbmc3k/error_pbmc_umap_5_min_dist_0.8.rds")
error_pbmc_umap3 <- read_rds("data/pbmc3k/error_pbmc_umap_5_min_dist_0.8.rds")
error_pbmc_tsne <- read_rds("data/pbmc3k/error_pbmc_tsne_5.rds")
error_pbmc_tsne2 <- read_rds("data/pbmc3k/error_pbmc_tsne_30.rds")
error_pbmc_phate <- read_rds("data/pbmc3k/error_pbmc_phate_5.rds")
error_pbmc_trimap <- read_rds("data/pbmc3k/error_pbmc_trimap_12_4_3.rds")
error_pbmc_pacmap <- read_rds("data/pbmc3k/error_pbmc_pacmap_30_random_0.9_5.rds")

@@

```{r}
#| echo: false
#| fig-cap: "Compare the published \\gD{} layout (@fig-pbmc-mse a) and the \\gD{} layout selected (@fig-pbmc-mse e) by MSE plot (@fig-pbmc-mse) from the UMAP and tSNE with default hyper-parameters. The PBMC3k data ($n =  2622$) has three close clusters in $9\\text{-}D$. Two \\gD{} projection from a tour on $9\\text{-}D$ of the model fit with @fig-pbmc-mse a ($a_1 = 0.06$, $b = 616/86 (22, 28)$) shows three-well separated clusters with big separations. On the other hand, the model fit with @fig-pbmc-mse e ($a_1 = 0.06$, $b = 704/227 (22, 32)$) shows three-well separated clusters with small separations. Therefore, @fig-pbmc-mse e is more reasonable than @fig-pbmc-mse a. Also, the fitted models in $9\\text{-}D$ help to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%

>>>>

- Make sure langevitour is explained before using it (introduced in page 5)
- Too much code needs to be streamlined
- Remove all the extraneous commented text (Done)
- Check how \kD{} and \gD{} are used, and make sure it's sensible
- Check spelling is consistently American
- Check references
- Add videos

@@

error_pbmc_umap <- read_rds("data/pbmc3k/error_pbmc_umap_30_min_dist_0.3.rds")
error_pbmc_umap2 <- read_rds("data/pbmc3k/error_pbmc_umap_5_min_dist_0.01.rds")
error_pbmc_umap3 <- read_rds("data/pbmc3k/error_pbmc_umap_5_min_dist_0.8.rds")
error_pbmc_tsne <- read_rds("data/pbmc3k/error_pbmc_tsne_5.rds")
error_pbmc_tsne2 <- read_rds("data/pbmc3k/error_pbmc_tsne_30.rds")
error_pbmc_phate <- read_rds("data/pbmc3k/error_pbmc_phate_5.rds")
error_pbmc_trimap <- read_rds("data/pbmc3k/error_pbmc_trimap_12_4_3.rds")
error_pbmc_pacmap <- read_rds("data/pbmc3k/error_pbmc_pacmap_30_random_0.9_5.rds")

@@

```{r}
#| echo: false
#| fig-cap: "Compare the published \\gD{} layout (@fig-pbmc-mse a) and the \\gD{} layout selected (@fig-pbmc-mse e) by MSE plot (@fig-pbmc-mse) from the UMAP and tSNE with default hyper-parameters. The PBMC3k data ($n =  2622$) has three close clusters in $9\\text{-}D$. Two \\gD{} projection from a tour on $9\\text{-}D$ of the model fit with @fig-pbmc-mse a ($a_1 = 0.06$, $b = 616/86 (22, 28)$) shows three-well separated clusters with big separations. On the other hand, the model fit with @fig-pbmc-mse e ($a_1 = 0.06$, $b = 704/227 (22, 32)$) shows three-well separated clusters with small separations. Therefore, @fig-pbmc-mse e is more reasonable than @fig-pbmc-mse a. Also, the fitted models in $9\\text{-}D$ help to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations are available at <https://youtu.be/3VfK3M2gnZM> and <> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%
